---
output: rmarkdown::github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r echo=FALSE, message=FALSE}
knitr::opts_chunk$set(message=FALSE, comment="#>")
devtools::load_all(".")
```

# rpkgs
A skeleton for R packages + Docker / Pkgdown / Pages aimed for Bioconductor

![.github/workflows/build.yaml](https://github.com/montilab/rpkgs/workflows/.github/workflows/build.yaml/badge.svg)
[![](https://img.shields.io/badge/lifecycle-maturing-4ba598.svg)](https://www.tidyverse.org/lifecycle/#maturing)

## Halp

Having trouble getting your package to build?

#### Build your Dockerfile locally

```bash
docker build --tag montilab/rpkgs:latest .
```

Does it build successfully?

#### See if the package is loadable on the image
```
docker run -i -t montilab/rpkgs:latest /bin/bash
R
library(rpkgs)
data(example)
print(example)
```

#### Build your github workflow file slowly and locally
```
# Install this tool for local testing
brew install nektos/tap/act

# List the actions
act -l

# Run the default (`push`) event:
act
```

## Documentation

Please visit <https://montilab.github.io/rpkgs/>

## Requirements

We recommend the latest version of R (\>= 4.0.0) but **rpkgs** currently requires R (\>= 3.6.0) to be installed.

## Installation

Install the development version of the package from Github.

``` r
devtools::install_github("montilab/rpkgs")
```

## Usage

```{r, eval=FALSE}
library(rpkgs)
```

```{r}
data(example)
print(example)
```

```{r}
cols <- colorize(example)
print(cols)
```

```{r}
visualize(cols)
```

```{r}
citation("rpkgs")
```
